\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{banking}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage[scale=0.87]{geometry}
\setlength{\hintscolumnwidth}{2.7cm}

% Personal data
\name{André}{Aigner}
\phone[mobile]{+49~174~6131721}
\email{andreaigner@icloud.com}
\social[linkedin]{andre-aigner}
\social[github]{a-aigner}
\address{}{Ergolding, Germany}{}

\begin{document}

\makecvtitle

% -------------------------
% SKILLS (Moved to Top)
% -------------------------
\section{Technical Skills}

\cvitem{Programming}{Python, JavaScript/TypeScript, C\#, Java, Swift, SQL}
\cvitem{Frameworks}{flutter, Spring Boot, Selenium, FastAPI, supabase}
\cvitem{DevOps \& Tools}{Docker, Git, Linux, REST APIs, Scikit-learn}
\cvitem{Specialties}{Software Development, Testing Automation, Microservices, Machine Learning, LLM Integration}

% -------------------------
% EXPERIENCE
% -------------------------
\section{Professional Experience}

\cventry{Oct 2025 -- Present}{Founder}{ARSoftware UG}{Landshut, Germany}{}{
\begin{itemize}
    \item Building and launching Apps focused on automation and AI-driven tooling.
    \item Managing full-stack development of software releases.
    \item Delivering custom software solutions and consulting services to SMEs.
\end{itemize}}

\cventry{Mar 2023 -- Aug 2025}{Working Student – IT Consulting}{intellior GmbH}{Stuttgart, Germany}{}{
\begin{itemize}
    \item Developed and deployed \textbf{5+ microservices} with API integrations used for data migrations with major German enterprises.
    \item Designed process-mining tools that improved business workflows by \textbf{~40\%}.
    \item Conducted database migrations with zero-downtime rollout.
    \item Worked with consulting partners and German banks on enterprise software integration and runtime optimization.
\end{itemize}}

\cventry{Apr 2022 -- Nov 2022}{Intern – Production Technologies}{BMW Group}{Dingolfing, Germany}{}{
\begin{itemize}
    \item Participated in innovation project with \textbf{Intel, NTT Data, Microsoft, and Ubisense}.
    \item Built Python automation scripts reducing manual process effort by \textbf{several hours per week}.
    \item Improved team workflows and supported data-driven production improvements.
\end{itemize}}

\cventry{Mar 2021 -- Mar 2022}{Software Developer (Student Worker)}{TRIO Project I}{Landshut, Germany}{}{
\begin{itemize}
    \item Developed a generic Selenium automation bot in C\# for large-scale UI testing.
\end{itemize}}

% -------------------------
% EDUCATION
% -------------------------
\section{Education}

\cventry{Oct 2025 -- Expected 2027}{M.Sc. Applied Artificial Intelligence}{TH Rosenheim}{Rosenheim, Germany}{}{}

\cventry{Mar 2023 -- Sep 2025}{B.Sc. Computer Science}{OTH Regensburg}{Regensburg, Germany}{}{
\textbf{Graduated successfully}
}

\cventry{Sep 2019 -- Mar 2023}{Computer Science Studies}{University of Applied Sciences Landshut}{Landshut, Germany}{}{
\begin{itemize}
    \item Served one year as \textbf{President of the Student Council}
\end{itemize}}

% -------------------------
% PROJECTS
% -------------------------
\section{Selected Projects}

\cvitem{\textbf{Aeneis Python API Wrapper}}{Developed a stable Python client library for Aeneis (intellior GmbH), enabling one of Germany’s largest business groups to integrate business-process data into an internal \textbf{AI/LLM chatbot system}.\\
\textit{Tech: Python, REST APIs, OAuth2} \\
GitHub: \url{https://github.com/a-aigner/aen_client}
}
\end{document}
